---
title: "TIRAD"
author: "kittipos sirivongrungson"
date: '2022-07-18'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(eval = F)
here::i_am("tirad.Rmd")
library(here)
library(dplyr)
```

## Resources

- [TIRADS Original](https://www.acr.org/Clinical-Resources/Reporting-and-Data-Systems/TI-RADS)

- [TIRADS-Calc by RadCalc](https://radcalculators.org/acr-tirads-calculator-for-thyroid-ultrasound/)

## Design

### Main Fn: `TIRADS_calc`

**Output** (List): 

-   Points
-   TIRADS Level (+ descriptions)
-   Recommendation

### Secondary Fn: `get_TIRADS_points`

**Output** (numeric): TIRADS Points 

Function’s Parameter

-   **composition** (chr): internal components of a nodule. 

  -   `cystic`: cystic or almost completely cystic (0)
  -   `spongiform`: microcystic component > 50% of the nodule volume (0)
  -   `mixed`: (1)
  -   `solid`: (2)

-   **echogenicity** (chr): level of echogenicity of the solid part, relative to surrounding thyroid tissue.

  -   `an` (0)
  -   `hyper` (1)
  -   `iso` (1)
  -   `hypo` (2)
  -   `very-hypo` (3)
  
  
-   **shape** (chr): 

  -   `wider` (0): wider-than-tall
  -   `taller` (3): taller-than-wide
  
-   **margin** (chr):

  -   `smooth` (0)
  -   `ill-defined` (0)
  -   `lobulated` (2)
  -   `irregular` (2)
  -   `extra` (3)
  
  
-   **echogenic_foci** (Checkboxes)

  -   `none` (0)
  -   `comet` (0)
  -   `macro-calc` (1)
  -   `rim-calc` (2)
  -   `punctate` (3)
  
  
## Function: `get_TIRADS_points`


```{r get_TIRADS_points}
get_TIRADS_points <- function(
    composition,
    echogenicity,
    shape,
    margin,
    echogenic_foci
    ) {
  
  ## Match Args
  
  composition <- rlang::arg_match(
    composition, c("cystic", "spongiform","mixed", "solid")
    )
  echogenicity <- rlang::arg_match(
    echogenicity, c("an", "hyper", "iso", "hypo", "very-hypo")
    )
  shape <- rlang::arg_match(shape, c("wider", "taller"))
  margin <- rlang::arg_match(
    margin, c("smooth", "ill-defined", "lobulated", "irregular", "extra")
    )
  echogenic_foci <- rlang::arg_match(
    echogenic_foci, values = c("none", "comet", "macro-calc", 
                               "rim-calc", "punctate"),
    multiple = TRUE # Can ≥ 1
    ) 
  
  if(any(duplicated(echogenic_foci))) cli::cli_abort("Value of {.code echogenic_foci} can not be duplicated.")
  
  
  pt <- vector("integer") # Init Empty Vector to Store
  
  pt["composition"] <- 
    switch (composition,
    "cystic" = 0L,
    "spongiform" = 0L,
    "mixed" = 1L,
    "solid" = 2L
  )
  
  pt["echogenicity"] <- 
    switch (echogenicity,
      "an" = 0L,
      "hyper" = 1L,
      "iso" = 1L,
      "hypo" = 2L,
      "very-hypo" = 3L
    )
  
  pt["shape"] <- 
    switch (shape,
      "wider" = 0L,
      "taller" = 3L
    )
  
  pt["margin"] <- 
    switch (margin,
      "smooth" = 0L,
      "ill-defined" = 0L,
      "lobulated" = 2L,
      "irregular" = 2L,
      "extra" = 3L
    )
  
  ## Echogenic Foci (Multi-select)
  foci <- c("none" = 0L, "comet" = 0L, "macro-calc" = 1L, 
            "rim-calc" = 2L, "punctate" = 3L)
  
  pt["echogenic_foci"] <- sum(foci[echogenic_foci])
  
  ## Combine Output
  list(points = pt,
       args = list(composition = composition,
                   echogenicity = echogenicity,
                   shape = shape,
                   margin = margin,
                   echogenic_foci = echogenic_foci)
       )
}

get_TIRADS_points("mixed", "iso", "taller", "smooth", 
                  c("none", "macro-calc"))
```




```{r}
x <- c(a = 1, b = 2, "c-1"=5)

x[c("a", "c-1")]

any(duplicated(c("a", "a")))
```





